Finding Quality Issues in SKOS Vocabularies

### 2012-03-30 conclusions.tex
polished conclusion

@@

We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary. To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront taxonomists with our results. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service. For larger vocabularies we also need to increase the performance and efficiency of our quality checking algorithms.

>>>>

We are aware that these issues are purely quantitative indicators and not statements about the quality of a vocabulary. To learn more about the real-world impact of our work, we will conduct a qualitative follow-up study, in which we discuss these results with more taxonomists. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service. We also need to increase the performance and efficiency of our quality checking algorithms.

@@
